\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-24 notes/2loopNLSM.tex
Fixed broken cites, slightly improved \citepls

%TODO-type commands
\newcommand\citepls{{\bf\color{red}[[Cite Needed]]}}
\newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}

@@

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{}. We will briefly review the perturbative construction of this theory below. 
\subsection{Color-dual Amplitudes}
Review of BCJ relations and Jacobi relations off-shell. Justify kinematic algebra in an off-shell framework by talking about on-shell construction. yada yada yada

@@

\subsubsection{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):

@@

\subsubsection{YZ-Theory}
SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung2016prv}.

@@

While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization. Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions. As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.

@@

\be
\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \epsilon_{(12)} \epsilon_{(34)}
\ee
One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
\be
\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
\ee
While introducing succesively higher spiin states to the NMHV lagrangian constructed in \cite{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above. This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations. 
\subsection{Block Decomposition of Yang-Mills}
Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory. All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite:
\begin{eBox}
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
\end{eBox}
By a simple mass-dimensioin argument, we know the tree-level cubic sector is simply:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
and likewise at one-loop:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
We can select out both of these manifestly cubic sectors by selecting only $\epsilon^+\epsilon^+$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states. Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
\be
A(...,\bar{J}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
\ee
and similarly so at one-loop:
\be
A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
\ee
To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
\begin{eBox}
\be
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\epsilon\rightarrow k}
\ee
\end{eBox}
Why must we take the derivative with respect to $D$? After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes. However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit. We will construct these one-loop integrands below in the next section. 
\subsection{One-loop SDYM Integrands}
\be
\simplebox = g_{\text{YM}}^4 X(k_1,l_1)X(k_2,l_2)X(k_3,l_3)X(k_4,l_4)
\ee
\subsection{One-loop NLSM Integrands}

>>>>

%TODO-type commands
\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed:#1]]}}
\newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}

@@

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}. We will briefly review the perturbative construction of this theory below. 
\subsection{Color-dual Amplitudes}
Review of BCJ relations and Jacobi relations off-shell. Justify kinematic algebra in an off-shell framework by talking about on-shell construction. yada yada yada

@@

\subsubsection{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):

@@

\subsubsection{YZ-Theory}
SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.

@@

While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization. Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions. As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.

@@

\be
\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \epsilon_{(12)} \epsilon_{(34)}
\ee
One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
\be
\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
\ee
While introducing succesively higher spiin states to the NMHV lagrangian constructed in \citepls{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above. This is easily understood in terms of a polarization decomposition introduced by one of the authors \citepls{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations. 
\subsection{Block Decomposition of Yang-Mills}
Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory. All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \citepls{}:
\begin{eBox}
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
\end{eBox}
By a simple mass-dimensioin argument, we know the tree-level cubic sector is simply:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
and likewise at one-loop:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
We can select out both of these manifestly cubic sectors by selecting only $\epsilon^+\epsilon^+$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states. Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
\be
A(...,\bar{J}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
\ee
and similarly so at one-loop:
\be
A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
\ee
To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
\begin{eBox}
\be
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\epsilon\rightarrow k}
\ee
\end{eBox}
Why must we take the derivative with respect to $D$? After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes. However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit. We will construct these one-loop integrands below in the next section. 
\subsection{One-loop SDYM Integrands}
\be
\simplebox = g_{\text{YM}}^4 X(k_1,l_1)X(k_2,l_2)X(k_3,l_3)X(k_4,l_4)
\ee
\subsection{One-loop NLSM Integrands}
